---
title: "lab4.2 - Confidence Intervals - Nhi Nguyen"
output: pdf_document

---

Background Information:

```{r}
load('yrbss.rda')
```

Calculating confidence intervals:
1.
```{r}
yrbss.complete = yrbss[complete.cases(yrbss$weight), ]
sample.size = 30
set.seed(5011)

sample.rows = sample(1:nrow(yrbss.complete), sample.size)

yrbss.sample = yrbss.complete[sample.rows, ]

summary(yrbss.sample$weight)
```

QUES a:
```{r}
mean.sample = mean(yrbss.sample$weight) #calculate the mean of sample
sd.sample = sd(yrbss.sample$weight) #calculate the standard deviation of the sample
```

QUES b:
```{r}
z = qnorm(0.975,)
z
```

QUES c:
margin error of x:
```{r}
margin.error = z * sd.sample / sqrt(sample.size)
margin.error

margin.left = mean.sample - margin.error
margin.right = mean.sample + margin.error

cat("(", margin.left,",", margin.right,")")
```

QUES d:
when the sd value is getting bigger, the confidence interval is getting larger

2.
QUES a:
```{r}
z.90 = qnorm(1-(1-0.9)/2,)

margin.error = z.90 * sd.sample / sqrt(sample.size)
margin.error

margin.left = mean.sample - margin.error
margin.right = mean.sample + margin.error

cat("(", margin.left,",", margin.right,")")
```

QUES b:
```{r}
z.99 = qnorm(1-(1-0.99)/2,)

margin.error = z.99 * sd.sample / sqrt(sample.size)
margin.error

margin.left = mean.sample - margin.error
margin.right = mean.sample + margin.error

cat("(", margin.left,",", margin.right,")")
```

QUES c:
90% CI: ( 64.1431 , 75.1129 )
95% CI: ( 63.09234 , 76.16366 )
99% CI: ( 61.03869 , 78.21731 )
90% CI is the biggest interval, followed by 95% CI then 99% CI.

QUES d:
the larger the confidence level is, the bigger the confidence interval is respectively. however, when the CL reach the absolute value (100%), the CI varies with every value because it doesnt have meaningful value for prediction. CI with CL 90% is the most informative.

3.
QUES a:
```{r}
yrbss.complete = yrbss[complete.cases(yrbss$weight), ]
sample.size = 30
set.seed(5011)

sample.rows = sample(1:nrow(yrbss.complete), sample.size)

yrbss.sample = yrbss.complete[sample.rows, ]

t.test(yrbss.sample$weight, conf.level = 0.95) $conf.int
```

QUES b:
```{r}
yrbss.complete = yrbss[complete.cases(yrbss$weight), ]
sample.size = 50
set.seed(5011)

sample.rows = sample(1:nrow(yrbss.complete), sample.size)

yrbss.sample = yrbss.complete[sample.rows, ]

t.test(yrbss.sample$weight, conf.level = 0.95) $conf.int
```

```{r}
yrbss.complete = yrbss[complete.cases(yrbss$weight), ]
sample.size = 100
set.seed(5011)

sample.rows = sample(1:nrow(yrbss.complete), sample.size)

yrbss.sample = yrbss.complete[sample.rows, ]

t.test(yrbss.sample$weight, conf.level = 0.95) $conf.int
```

```{r}
yrbss.complete = yrbss[complete.cases(yrbss$weight), ]
sample.size = 300
set.seed(5011)

sample.rows = sample(1:nrow(yrbss.complete), sample.size)

yrbss.sample = yrbss.complete[sample.rows, ]

t.test(yrbss.sample$weight, conf.level = 0.95) $conf.int
```
